% Created 2014-03-30 Sun 21:46
\documentclass[11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{fixltx2e}
\usepackage{graphicx}
\usepackage{longtable}
\usepackage{float}
\usepackage{wrapfig}
\usepackage{rotating}
\usepackage[normalem]{ulem}
\usepackage{amsmath}
\usepackage{textcomp}
\usepackage{marvosym}
\usepackage{wasysym}
\usepackage{amssymb}
\usepackage{hyperref}
\tolerance=1000
\usepackage[margin=1in]{geometry}
\author{Josh Gordon <github@joshgordon.net>}
\date{2014-03-30}
\title{Weblights API Description}
\hypersetup{
  pdfkeywords={},
  pdfsubject={},
  pdfcreator={Emacs 24.3.1 (Org mode 8.2.1)}}
\begin{document}

\maketitle

\section{HTTP Requests you can make}
\label{sec-1}

\subsection{General}
\label{sec-1-1}
\begin{itemize}
\item \texttt{/on} Turns the lights on. (Fading them in)
\item \texttt{/off} Turns the lights off. (Fading them out)
\item \texttt{/desk/red/green/blue} Sets the desk lights (string A) to \texttt{red}, \texttt{green}, \texttt{blue}
\item \texttt{/a/red/green/blue} Shorthand for above.
\item \texttt{/window/red/green/blue} Sets the window lights (string B) to \texttt{red}, \texttt{green}, \texttt{blue}
\item \texttt{/b/red/green/blue} Shorthand for above.
\item \texttt{/work/brightness} Sets the worklight to \texttt{brightness}.
\item \texttt{/w/brightness} Shorthand for above.
\end{itemize}
\subsection{Fading}
\label{sec-1-2}
Adding \texttt{/fade} to the beginning of any of the above commands makes
them fade to that color in a reasonable amount of time. If you want to
specify the fade time, simply add \texttt{/fade/fadeTime/} to the beginning
of one of the above commands. 

\subsection{POST}
\label{sec-1-3}
You can post data, if you'd prefer that. (The default WebUI does.) You
have the following post fields. 

\textbf{N.B.:} If you post a value for red for a color, you MUST post Green
and Blue as well, otherwise you'll freak the python out.


The following post fields are valid: 
\begin{description}
\item[{a$_{\text{red}}$}] A's new red value
\item[{a$_{\text{grn}}$}] A's new green value
\item[{a$_{\text{blu}}$}] A's new blue value
\item[{a$_{\text{fad}}$}] A's fade time. (default: 0)

\item[{b$_{\text{red}}$}] B's new red value
\item[{b$_{\text{grn}}$}] B's new green value
\item[{b$_{\text{blu}}$}] B's new blue value
\item[{b$_{\text{fad}}$}] B's fade time. (default: 0)

\item[{w$_{\text{brt}}$}] W's new brightness
\item[{w$_{\text{fad}}$}] W's fade time. (default: 0)
\end{description}
% Emacs 24.3.1 (Org mode 8.2.1)
\end{document}
